Evaluating the Performance and Energy Efficiency of COSMO-ART, a Coupled Numerical Weather Forecast and Chemical Transport Model.

### 2014-04-23 paper_enahpc14/Sec3:Measurement-framework.tex
adds minor changes; updates paper.bib; includes references for related work

\subsubsection{E3METER metering products}
Supercomputer  clusters considered  for our  experiments at  the Swiss
National Supercomputing Center of  ETH Zurich (CSCS) are equipped with
E3METER Intelligent  Power Strips (IPS)  and Monitors (IPM)  which are
high   quality   electricity  meters   released   by  Riedo   Networks
(\url{http://riedonetworks.com/}),  that  enable  to monitor  and  log
power  consumption of  the  IT infrastructure  as  well as  constantly
analyze  line  voltage,  current,  power-factor,  frequency  with  1\%
accuracy.   Using reliable  narrowband  powerline communication  (PLC)
technology,  all metering  and power  quality data  from each  IPS are
centrally collected by the E3METER Data Concentrator, via the existing
power cables thus  avoiding the need for extra  cabling.  This data is
made  available  via SNMP,  HTTP,  TELNET  through  the built-in  Fast
Ethernet  port.   Time  synchronization  is guaranteed  by  using  NTP
servers.   Measured data  is accessed  through the  open  source Cacti
software including  the E3METER  Cacti Plugin to  scan the  entire PLC
network and monitor  in real-time the power usage  of individual rack,
recorded in 5 minutes interval periods.

\subsubsection{University of Hamburg}
To assess the  performance and the energy efficiency  of COSMO-ART, we
employ   a    version   of   the    integrated   framework   presented
in~\cite{energy13}  that  works in  combination  with Extrae  and
Paraver,   which  are   profiling/tracing   and  visualization   tools,
respectively.
%The left part of the \vref{fig:Lustre} offers a graphical representation of
%the Lustre architecture; the right depicts the tracing and profiling framework.
To  use our  approach,  COSMO-ART is  compiled  using the  Extrae
compiler wrappers, which automatically  instrument the Fortran code of
the  model. Next,  COSMO-ART is  run  on the  nodes, thus  dissipating
certain  amount of  power.  These  nodes are connected  to power 
measurement  devices that  account for  the dissipated power/consumed 
energy and  send the power data  to the tracing  server. The client, 
meanwhile, sends start/stop primitives in order to gather captured data
by the wattmeters onto the tracing server, where an  instance of the 
\pmlib server  is running.

Once COSMO-ART run is finished, a file containing the power profile is 
created using the  power   data  received from  the  tracing   server and
the  instrumentation post-processing generates  the performance trace files.
All these files are combined then in Paraver which allows us to visualize 
the performance trace and the power profile of COSMO-ART all together.

>>>>

\subsubsection{CSCS - E3METER metering products}
Supercomputer  clusters considered  for our  experiments at  the Swiss
National Supercomputing Center (CSCS)  of ETH Zurich are equipped with
E3METER Intelligent  Power Strips (IPS)  and Monitors (IPM)  which are
high   quality   electricity  meters   released   by  Riedo   Networks
(\url{http://riedonetworks.com/}),  that  enable  to monitor  and  log
power  consumption of  the  IT infrastructure  as  well as  constantly
analyze  line  voltage,  current,  power-factor,  frequency  with  1\%
accuracy.   Using reliable  narrowband  powerline communication  (PLC)
technology,  all metering  and power  quality data  from each  IPS are
centrally collected by the E3METER Data Concentrator, via the existing
power cables thus  avoiding the need for extra  cabling.  This data is
made  available  via SNMP,  HTTP,  TELNET  through  the built-in  Fast
Ethernet  port.   Time  synchronisation  is guaranteed  by  using  NTP
servers.   Measured data  is accessed  through the  open  source Cacti
software including  the E3METER  Cacti Plugin to  scan the  entire PLC
network and monitor  in real-time the power usage  of individual rack,
recorded in 5 minutes interval periods.

\subsubsection{UHAM - UJI}
To assess the  performance and the energy efficiency  of COSMO-ART, we
employ   a    version   of   the    integrated   framework   presented
in~\cite{energy13} that works in  combination with Extrae and Paraver,
which are profiling/tracing and visualization tools, respectively.

%The left part of the \vref{fig:Lustre} offers a graphical representation of
%the Lustre architecture; the right depicts the tracing and profiling framework.
To use our  approach, COSMO-ART is compiled using  the Extrae compiler
wrappers,  which  automatically instrument  the  Fortran  code of  the
model. Next, COSMO-ART  is run on the nodes,  thus dissipating certain
amount  of power.   These  nodes are  connected  to power  measurement
devices that account for the dissipated power/consumed energy and send
the power  data to the  tracing server.  The client,  meanwhile, sends
start/stop  primitives  in  order  to  gather  captured  data  by  the
watt-meters onto the  tracing server, where an instance  of the \pmlib
server is running.

Once COSMO-ART run is finished, a file containing the power profile is
created using the power data  received from the tracing server and the
instrumentation post-processing generates the performance trace files.
All  these files  are  combined then  in  Paraver which  allows us  to
visualise the performance trace and the power profile of COSMO-ART all
together.
